\Title

### 2021-02-16 manuscript/content.tex
Wrap long lines

\begin{enumerate}
  \item Define a set of $M$ equivalent sources distributed throughout the
    survey area (see section \ref{sec:source_distribution} for details).
  \item Define a set of $K$ overlapping windows of equal size that cover the
    survey area.
  \item Create $K$ separate sets of equivalent sources, one for each window.
    Each set will be formed by the portion of the original $M$ sources that fall inside
    the respective window.
    Since the windows overlap, the total number of sources
    from all sets will be greater than $M$.
  \item Define the vector $\mathbf{c}_k$ as the coefficients of the equivalent
    sources of the $k$-th window and matrix $\mathbf{A}_k$ as the Jacobian
    matrix between those sources and every data point of the survey.
  \item Model the predicted data as a superposition of the effects of the $K$
    separate sets of equivalent sources.
\end{enumerate}

>>>>

\begin{enumerate}
  \item Define a set of $M$ equivalent sources distributed throughout the
    survey area (Fig.~\ref{fig:gradient-boosting-schematics}b).
  \item Define a set of $K$ overlapping windows of equal size that cover the
    survey area.
  \item Create $K$ separate sets of equivalent sources, one for each window.
    Each set will be formed by the portion of the original $M$ sources that
    fall inside the respective window.
    Since the windows overlap, the total number of sources from all sets will
    be greater than $M$ (Fig.~\ref{fig:gradient-boosting-schematics}c).
  \item Define the vector $\mathbf{c}_k$ as the coefficients of the equivalent
    sources of the $k$-th window and matrix $\mathbf{A}_k$ as the Jacobian
    matrix between those sources and every data point of the survey.
  \item Model the predicted data as a superposition of the effects of the $K$
    separate sets of equivalent sources.
\end{enumerate}

\begin{figure*}
    \centering
    \includegraphics[width=0.8\linewidth]{figs/gradient-boosting-schematics.pdf}
    \caption{
        Sketch of the gradient-boosting process.
        (a)~Set of observation points that simulate a ground survey.
        (b)~Location of the sources obtained by putting one source below each
        observation point.
        (c)~Sets of equivalent sources obtained through gradient-boosting by
        selecting only the ones that fall inside each overlapping window.
        Blue and orange dots represent the horizontal location of the
        observation points and the original sources, respectively.
        The dashed line squares represent the boundaries of each overlapping
        window, while its corresponding sources are symbolized through red
        dots.
        Grey dots represent the other sources that aren't included in that
        particular set.
    }
    \label{fig:gradient-boosting-schematics}
\end{figure*}
